---
title: 'Final Project Spring 2022: Part 4'
author: "Di Zhang"
date: '2022-04-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages

```{r, load_packages}
library(tidyverse)
library(caret)
# install.packages('vip')
library(vip)
```

## Read and Prep Data

```{r, prep_data}
df_all <- readr::read_csv("final_project_train.csv", col_names = TRUE)

# data for linear regression
dfii <- df_all %>% 
  mutate(y = log(response)) %>% 
  select(region, customer, starts_with('x'), y)

# data for logistic regression
dfiii <- df_all %>% 
  select(-rowid, -response) %>%
  mutate(y = ifelse(outcome == "event", 1, 0))
```

# Project Part 4: Interpretation

# 4.1 Best performing models for linear regression and logistic regression
As previously identified in iiD and iiiD, we load the best performing models.
```{r, load_models}
pt2_svm <- readr::read_rds("svm_mod.rds")

pt3_mod06 <- readr::read_rds("pt3_mod06.rds")
```

We identify the most important variables associated with the best performing models respectively.

i) Linear regression
We define functions required for permutation based variance importance scores:
```{r}
mae <- function(actual, predicted) {
  mean(abs(actual - predicted))
}

pfun <- function(object, newdata) predict(object, newdata = newdata)
```

And calculate variance importance via the `vip::vip` method for `SVM` model.
```{r}
vip::vip(pt2_svm, method = "permute", pred_wrapper = pfun, target = "y", metric = "RMSE",
    train = dfii)
```
Despite the smallness of the importance scores overall, for `SVM` model, the most important variable appears to be region.

```{r}
plot(varImp(pt3_mod06), top = 20)
```
The most important variable for the best logistic regression model is `xn_03`.

`xs` inputs are not found to be the most important in either of the best models we found, though it is part of the top 20 important features for `glmnet` model featuring categorical region input interacting with all continuous inputs. Based on results thus far, we cannot determine if `xs` is helpful for prediction.