---
title: "Final Project Spring 2022: Part 1"
author: "Qinnuo Li, Di Zhang"
date: "3/29/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
Under construction.

## Load Packages

```{r, load_packages}
library(tidyverse)
library(visdat)
library(corrplot)
```

* `tidyverse` suite of packages is used throughout the entire project.  
* `visdat` is used in Part 1 to visually check for the missing values in the data frame. 
* `corrplot` is used to create correlation plot, to visualize the relationship between continuous inputs.  

## Read Data

```{r, read_data_01}
df_all <- readr::read_csv("final_project_train.csv", col_names = TRUE)
```

We first read in the data for the final project as a data frame. After running this code chunk we are informed that this data frame has 677 rows and 38 columns. Of the 38 columns, 3 are `chr` (string or character) data types and 35 are `dbl` (numeric) data types.  

## A Glimpse of the Data

We now take a "glimpse" of the data frame by calling the `glimpse()` function, to get a better idea of what those 38 columns look like - the variable names, their data types, as well as a snapshot of their values in the first few rows:  

```{r, read_data_02}
df_all %>% glimpse()
```

Combined with the final project guide, we understand that the 38 variables are divided into 3 categories: identifiers(`rowid`, `region` and `customer`), sentiment derived features(columns start with `x`), and outputs(`response` and `outcome`). putting all the columns together, one row of the data frame corresponds to a product sold to a customer.  

We will ignore `rowid` as it's used only for book-keeping purposes. Among the identifiers, `region` and `customer` are both categorical. The sentiment derived features are continuous variables. `response` is a continuous output representing the average hours per week associated with a product sold to a customer; `outcome` is a categorical output that takes on the value of either "event" or "non_event", with "event" representing the product did NOT achieve its sales goal.  

# Project Part 1: Exploration

## 1.1 Check for missing values

We first visually check for missing values in the data frame using the `visdat` package.  
```{r, pt01_sec01}
visdat::vis_miss(df_all)
```

We confirm that there is no missing values, as all data are present.  

## 1.2 Check for unique values per variable

We then check for the number of unique values per variable.  
```{r, pt01_sec02}
df_all %>% purrr::map_dbl(n_distinct)
```

Here we are seeing the categorical variables have few distinct values. Let's use the `count()` function to reveal the levels for each variable and the counts associated with each level, and plot a bar chart to visualize the distribution of the categorical variables.  

## 1.3 Visualize the distribution of variables - counts for categorical variables

```{r, pt01_sec03_region}
df_all %>% count(region)
df_all %>% ggplot(mapping = aes(x = region)) + geom_bar()
```

Executing the above code chunk reveals there are three regions, `xx`, `yy`, and `zz`, where `xx` appears `r count(df_all$region = xx)` times in the data set, `yy` `r count(df_all$region = yy)` times, and `zz` `r count(df_all$region = zz)` times.  

```{r, pt01_sec03_customer}
df_all %>% count(customer)
df_all %>% ggplot(mapping = aes(x = customer)) + geom_bar()
```

There are 9 customers in total, including a lumped `Other`. Among the 9 customers, `G`, `M`, and `Other` appear in the data set more than 60 times, while `A`, `B`, `D`, `E`, `K`, `Q` appear less than 60 times.  

```{r, pt01_sec03_outcome}
df_all %>% count(outcome) %>% mutate(prop = n / sum(n))
df_all %>% ggplot(mapping = aes(x = outcome)) + geom_bar()
```

In this data set `outcome` is imbalanced, with the empirical event frequency being about 19%, meaning that the event is observed 19% out of all observations, and 81% of the time non-event is observed.  

## 1.4 Visualize the distribution of variables - distribution for continuous variables

To better visualize the distribution of the continuous variable, we will print out the summary statistics, and plot a boxplot to visualize the span of variable values, examining if they are on the similar scale, and help us later decide if pre-processing inputs are necessary. We will then plot a histogram to visualize the distribution of the values to understand where are the values concentrated over the span of all observations. Since we have a decent number of input variables, we will split them according to the naming into `xb` related, `xn` related, `xa` related, `xw` related, and `xs` related, so we only need to focus on a handful of plots at a time.  

After we are done exploring the distribution of each sentiment derived features, in the order of `xb_`, `xn_`, `xa_`, `xw_`, and `xs_`. We will examine the distribution for `response` at the end to finish up the exploration for continuous variables.    

```{r, pt01_sec04_xb_summary}
df_all %>% 
  select(all_of(starts_with("xb_"))) %>%
  summary()
```

```{r, pt01_sec04_xb_boxplots}
df_all %>% 
  select(all_of(starts_with("xb_"))) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  mutate(input_id = stringr::str_extract(name, "\\d+")) %>%
  mutate(input_id = as.numeric(input_id)) %>%
  ggplot(mapping = aes(x = input_id, y = value)) +
  geom_boxplot(fill = "grey",
               mapping = aes(group = input_id))
```


```{r, pt01_sec04_xb_histogram}
df_all %>% 
  select(all_of(starts_with("xb_"))) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  ggplot(mapping = aes(x = value)) +
  geom_histogram(bins = 35) +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank())
```

Looking at the boxplot for `xb_` features, their values are distributed on a similar scale. They do have varied distributions, however. `xb_02` and ``xb_03` looks like they are taking on discrete values along the x-axis. Among the total of 8 `xb_` features `xb_01` and `xb_04` vaguely assemble a Gaussian distribution.  

```{r, pt01_sec04_xn_summary}
df_all %>% 
  select(all_of(starts_with("xn_"))) %>%
  summary()
```

```{r, pt01_sec04_xb_boxplots}
df_all %>% 
  select(all_of(starts_with("xn_"))) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  mutate(input_id = stringr::str_extract(name, "\\d+")) %>%
  mutate(input_id = as.numeric(input_id)) %>%
  ggplot(mapping = aes(x = input_id, y = value)) +
  geom_boxplot(fill = "grey",
               mapping = aes(group = input_id))
```

```{r, pt01_sec04_xn_histogram}
df_all %>% 
  select(all_of(starts_with("xn_"))) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  ggplot(mapping = aes(x = value)) +
  geom_histogram(bins = 35) +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank())
```

As with `xb_` features, from the boxplot `xn_` also have all their values concentrated on a smaller scale, roughly from -5 to 10. As with the histograms it's worth noting that `xn_02` and `xn_03` both take on discrete values on the x-axis while the rest seem to be continuous.  

```{r, pt01_sec04_xa_summary}
df_all %>% 
  select(all_of(starts_with("xa_"))) %>%
  summary()
```

```{r, pt01_sec04_xa_boxplots}
df_all %>% 
  select(all_of(starts_with("xa_"))) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  mutate(input_id = stringr::str_extract(name, "\\d+")) %>%
  mutate(input_id = as.numeric(input_id)) %>%
  ggplot(mapping = aes(x = input_id, y = value)) +
  geom_boxplot(fill = "grey",
               mapping = aes(group = input_id))
```

```{r, pt01_sec04_xa_histogram}
df_all %>% 
  select(all_of(starts_with("xa_"))) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  ggplot(mapping = aes(x = value)) +
  geom_histogram(bins = 35) +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank())
```

From the boxplot `xa_` features take on a larger range of values compared to `xb_` and `xn_`, in the range of (-10, 40). The histogram shows that all values are continuous. No feature is discrete.  

```{r, pt01_sec04_xs_summary}
df_all %>% 
  select(all_of(starts_with("xs_"))) %>%
  summary()
```

```{r, pt01_sec04_xs_boxplots}
df_all %>% 
  select(all_of(starts_with("xs_"))) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  mutate(input_id = stringr::str_extract(name, "\\d+")) %>%
  mutate(input_id = as.numeric(input_id)) %>%
  ggplot(mapping = aes(x = input_id, y = value)) +
  geom_boxplot(fill = "grey",
               mapping = aes(group = input_id))
```

```{r, pt01_sec04_xs_histogram}
df_all %>% 
  select(all_of(starts_with("xs_"))) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  ggplot(mapping = aes(x = value)) +
  geom_histogram(bins = 35) +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank())
```

`xs_` has a much smaller span, over (-1, 2). And with the `xs_` features, all except `xs_05` and `xs_06` looks roughly Gaussian - `xs_05` and `xs_06` are right-skewed. 

```{r, pt01_sec04_xw_summary}
df_all %>% 
  select(all_of(starts_with("xw_"))) %>%
  summary()
```

```{r, pt01_sec04_xw_boxplots}
df_all %>% 
  select(all_of(starts_with("xw_"))) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  mutate(input_id = stringr::str_extract(name, "\\d+")) %>%
  mutate(input_id = as.numeric(input_id)) %>%
  ggplot(mapping = aes(x = input_id, y = value)) +
  geom_boxplot(fill = "grey",
               mapping = aes(group = input_id))
```

```{r, pt01_sec04_xw_histogram}
df_all %>% 
  select(all_of(starts_with("xw_"))) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  ggplot(mapping = aes(x = value)) +
  geom_histogram(bins = 35) +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank())
```

`xw_` has all observations span over (0, 105). From the histogram, `xw_01` looks like a normal distribution, `xw_02` has a lot of 0's, and `xw_03` is left-skewed, having a lot of values concentrated on the range greater than 90.  

Given all the boxplots and histograms created so far, we conclude that pre-processing the inputs is preferred in the project as different groups of features have different scales, and some of them are highly skewed.

We will now move on to examine the distribution of the continuous output `response`.  

```{r, pt01_sec04_response_summary}
df_all %>% 
  select(response) %>%
  summary()
```

```{r, pt01_sec04_response_histogram}
df_all %>% 
  select(response) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  ggplot(mapping = aes(x = value)) +
  geom_histogram(bins = 35) +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank())
```

The `response` is right-skewed, with most of it values concentrated on the [0, 5] interval and some extreme values on the right-hand side forming a long tail.  

In this session we have looked at the distributions and scales are the continuous inputs and the continuous output `response`. We have noticed quite a few variables have highly skewed distribution, such as `xw_02`, `xw_03`, and `xs_05`. Therefore preprocessing, and specifically center and scale the continuous inputs are necessary for this project.

The continuous output `response` is also highly right-skewed, and we decide that we will perform a log-transformation on `reponse`, and use the transformed output in our model training and evaluation process.  

## 1.5 Conditioning the continuous variables based on the categorical variables

## 1.5.1 Condition the continuous inputs on REGION

Let's now condition the input distributions by the `region` level.  

```{r, pt01_sec05_region}
df_all %>% 
  select(-rowid, -customer, -outcome, -response) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid", "region")) %>% 
  ggplot(mapping = aes(x = region, y = value)) +
  geom_boxplot(mapping = aes(fill = region,
                             color = region),
               alpha = 0.33) +
  facet_wrap(~name, scales = "free_y") +
  scale_fill_brewer(guide = 'none', palette = 'Set1') +
  scale_color_brewer(guide = 'none', palette = 'Set1') +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

For `xb`, `xa`, `xn`,  and `xs` set of features, the boxes for each region all overlap with each other and are roughly at the same level. The set for `xw` is worth noting where region `ZZ` has a noticibally larger span of quantiles, indicating the values can be more uncertainty.  

## 1.5.2 Condition the continuous inputs on CUSTOMER

```{r, pt01_sec05_customer}
df_all %>% 
  select(-rowid, -region, -outcome, -response) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid", "customer")) %>% 
  ggplot(mapping = aes(x = customer, y = value)) +
  geom_boxplot(mapping = aes(fill = customer,
                             color = customer),
               alpha = 0.33) +
  facet_wrap(~name, scales = "free_y") +
  scale_fill_brewer(guide = 'none', palette = 'Set1') +
  scale_color_brewer(guide = 'none', palette = 'Set1') +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())

```

Here in `xw` the boxes are a lot more longer compared to those for other features, the range between the first and third quantile is much larger. The median also varies a lot compared to other facets.  

## 1.5.3 Condition the continuous inputs on OUTCOME

```{r, pt01_sec05_outcome}
df_all %>% 
  select(-rowid, -region, -customer, -response) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid", "outcome")) %>% 
  ggplot(mapping = aes(x = value)) +
  geom_freqpoly(mapping = aes(y = stat(density), color = outcome),
                size = 1, bins = 21) +
  facet_wrap(~name, scales = "free") +
  scale_color_brewer(palette = "Set1") +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

The frequency polygon for `event` and `non-event`, for most features, share similar shapes and have overlaps with each other. Some places it's difficult to tell the two apart. Among the five sets of features, the frequency polygon for `event` and `non-event` in `xn` is the most distinct and the easiest to tell the two apart. This indicates that `xn` might be very helpful in helping the model pick up trends and make predictions.  

## 1.6 Visualize the correlation between the continuous inputs

```{r, pt01_sec06_corr}
df_all %>% 
  select(all_of(starts_with("x"))) %>% 
  cor() %>% 
  corrplot::corrplot(method = 'square', type = 'upper')
```
The correlation plot above reveals patterns of high correlation, no correlation, and anti-correlation between the inputs. We can, however, rearrange the variables and group correlated variables together to get a better sense of the grouping structure within the data using hierarchical clustering.

```{r, pt01_sec06_hclust}
df_all %>% 
  select(all_of(starts_with("x"))) %>% 
  cor() %>% 
  corrplot::corrplot(method = 'square', type = 'upper',
                     order = 'hclust', hclust.method = 'ward.D2')
```

Looking at this hierarchical clustered correlation plot, there does exist high correlation and anti-correlation between the features. For cells close to the main diagonal line there are squares with dark blue, representing high correlations; there are also less than 10 cells with relatively dark red color, indicating a moderate anti-correlation.  

## 1.7 Visualize the behavior of the continuous outputs with respect to the continuous inputs

```{r, pt01_sec07_xb_response, eval=TRUE}
df_all %>% 
  select(starts_with("xb_"), response) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(starts_with("xb_")) %>% 
  ggplot(mapping = aes(x = value, y = log(response))) +
  geom_point() +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

```{r, pt01_sec07_xa_response, eval=TRUE}
df_all %>% 
  select(starts_with("xa_"), response) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(starts_with("xa_")) %>% 
  ggplot(mapping = aes(x = value, y = log(response))) +
  geom_point() +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

```{r, pt01_sec07_xn_response, eval=TRUE}
df_all %>% 
  select(starts_with("xn_"), response) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(starts_with("xn_")) %>% 
  ggplot(mapping = aes(x = value, y = log(response))) +
  geom_point() +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

```{r, pt01_sec07_xs_response, eval=TRUE}
df_all %>% 
  select(starts_with("xs_"), response) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(starts_with("xs_")) %>% 
  ggplot(mapping = aes(x = value, y = log(response))) +
  geom_point() +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

```{r, pt01_sec07_xn_response, eval=TRUE}
df_all %>% 
  select(starts_with("xn_"), response) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(starts_with("xn_")) %>% 
  ggplot(mapping = aes(x = value, y = log(response))) +
  geom_point() +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

## 1.8 Visualize the behavior of the binary outcome with respect to the continuous inputs

```{r, pt01_sec08_xb_outcome, eval=TRUE}
df_all %>% 
  select(starts_with("xb_"), outcome) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(starts_with("xb_")) %>% 
  ggplot(mapping = aes(x = value, y = outcome)) +
  geom_point() +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

```{r, pt01_sec08_xa_outcome, eval=TRUE}
df_all %>% 
  select(starts_with("xa_"), outcome) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(starts_with("xa_")) %>% 
  ggplot(mapping = aes(x = value, y = outcome)) +
  geom_point() +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

```{r, pt01_sec08_xn_outcome, eval=TRUE}
df_all %>% 
  select(starts_with("xn_"), outcome) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(starts_with("xn_")) %>% 
  ggplot(mapping = aes(x = value, y = outcome)) +
  geom_point() +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

```{r, pt01_sec08_xs_outcome, eval=TRUE}
df_all %>% 
  select(starts_with("xs_"), outcome) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(starts_with("xs_")) %>% 
  ggplot(mapping = aes(x = value, y = outcome)) +
  geom_point() +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

```{r, pt01_sec08_xb_outcome, eval=TRUE}
df_all %>% 
  select(starts_with("xw_"), outcome) %>%
  tibble::rowid_to_column() %>% 
  pivot_longer(starts_with("xw_")) %>% 
  ggplot(mapping = aes(x = value, y = outcome)) +
  geom_point() +
  facet_wrap(~ name, scales = "free") +
  theme(axis.text.y = element_blank(),
        strip.background = element_blank())
```

Looking at the graphs of the behavior of the outcome with respect to the continuous inputs, no linear separability is found in anyone of them.  